Azithromycin

### 2021-03-06 r_notebooks/preparing_differences/preparing_ace_inhib.Rmd
Edited preparing_ files. arima interpolation, init 36 months, 8 month horizon, excluded Jan and Feb 2020 from training

```{r ace-data}
gp <- 
  read_rds("../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as_factor(practiceid)) %>% 
  ungroup() %>% 
  janitor::clean_names() %>% 
  select(practice_id, year, npat)

ace <- 
  read_rds("../data/presdata_updates_040121/presc_wales_ace-inhibitors.rds") %>% 
  janitor::clean_names() %>% 
  mutate(datename = dmy(paste0("28-", datename)),
         practice_id = as_factor(practice_id))

@@

## Identify GPs with missing data 
gp_missing <- 
  ace_monthly_quantity_gp %>% 
  as_tibble() %>% 
  pivot_wider(id_cols = regional_unit, names_from = datename,
              values_from = n, values_fill = NA) %>% 
  rowwise() %>% 
  mutate(across(.cols = `2015 Jan`:`2020 Aug`, .fns = is.na)) %>% 
  group_by(regional_unit) %>% 
  summarise(miss_non_covid = sum(c_across(`2015 Jan`:`2020 Feb`)),
            miss_covid = sum(c_across(`2020 Mar`:`2020 Aug`))) %>% 
  filter(miss_covid > 0 | miss_non_covid > 0) %>% 
  mutate(miss_10_non_covid = if_else(miss_non_covid > 62/10, TRUE, FALSE))

@@

## Sort into monthly count data pre-lockdown (March 2020) as training data
ace_monthly_count_pre_cv19 <- 
  ace_monthly_count %>% 
  filter(datename < yearmonth(dmy("01-03-2020")))

ace_monthly_quantity_gp_pre_cv19 <- 
  ace_monthly_quantity_gp %>% 
  filter(datename < yearmonth(dmy("01-03-2020")))

## Replace missing values in training data
ace_monthly_count_pre_cv19 <- 
  ace_monthly_count_pre_cv19 %>% 
  model(mean = MEAN(n)) %>%
  interpolate(ace_monthly_count_pre_cv19)

ace_monthly_quantity_gp_pre_cv19 <- 
  ace_monthly_quantity_gp_pre_cv19%>% 
  group_by(regional_unit) %>% 
  model(mean = MEAN(n)) %>% 
  interpolate(ace_monthly_quantity_gp_pre_cv19)

@@

```{r, ace-gp-practice-modelling}
plan(cluster)
system.time(ace_gp_cv_models <-
  ace_monthly_quantity_gp_pre_cv19 %>%
                  regionalCV(init = 48, step = 3))
plan(sequential)

ace_gp_cv_models %>%
  saveRDS("../data/ace_gp_cv_models.rds")

ace_gp_cv_models <- 
  read_rds("../data/ace_gp_cv_models.rds")

ace_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  ggplot(aes(x = MAPE)) +
  geom_histogram() +
  xlim(0,100)

ace_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  group_by(.model) %>% 
  count() %>% 
  arrange(desc(n))

@@

```{r ace-gp-modelling-accuracy}
best_model_gp <- 
  ace_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE)

@@

```{r ace-gp-practice-forecasts}
plan(cluster)
system.time(ace_gp_fcsts <-
              ace_monthly_quantity_gp_pre_cv19 %>%
              filter(!regional_unit %in% best_mape_over_50$regional_unit) %>%
              regionalJointFcsts(h = "6 months"))
plan(sequential)

ace_gp_fcsts %>%
  saveRDS("../data/ace_gp_fcsts.rds")

ace_gp_fcsts <- 
  read_rds("../data/ace_gp_fcsts.rds")

@@

```{r, ace-gp-practice-discrepancies-abs}
best_model_gp <- 
  ace_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  filter(MAPE < 50)

@@

best_model_gp_discrep %>% 
  saveRDS("../data/differences/ace_discreps.rds")
```

>>>>

```{r ace-data}
gp <- 
  read_rds("../../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as_factor(practiceid)) %>% 
  ungroup() %>% 
  janitor::clean_names() %>% 
  select(practice_id, year, npat)

ace <- 
  read_rds("../../data/presdata_updates_040121/presc_wales_ace-inhibitors.rds") %>% 
  janitor::clean_names() %>% 
  mutate(datename = dmy(paste0("28-", datename)),
         practice_id = as_factor(practice_id))

@@

## Identify GPs with missing data 
gp_missing <- 
  ace_monthly_quantity_gp %>% 
  as_tibble() %>% 
  pivot_wider(id_cols = regional_unit, names_from = datename,
              values_from = n, values_fill = NA) %>% 
  rowwise() %>% 
  mutate(across(.cols = `2015 Jan`:`2020 Aug`, .fns = is.na)) %>% 
  group_by(regional_unit) %>% 
  summarise(miss_non_covid = sum(c_across(`2015 Jan`:`2020 Feb`)),
            miss_covid = sum(c_across(`2020 Mar`:`2020 Aug`))) %>% 
  filter(miss_covid > 0 | miss_non_covid > 0) %>% 
  mutate(miss_10_non_covid = if_else(miss_non_covid > 60/10, TRUE, FALSE))

@@

## Sort into monthly count data pre-lockdown (March 2020) as training data
ace_monthly_count_pre_cv19 <- 
  ace_monthly_count %>% 
  filter(datename < yearmonth(dmy("01-01-2020")))

ace_monthly_quantity_gp_pre_cv19 <- 
  ace_monthly_quantity_gp %>% 
  filter(datename < yearmonth(dmy("01-01-2020")))

## Replace missing values in training data
ace_monthly_count_pre_cv19 <- 
  ace_monthly_count_pre_cv19 %>% 
  model(mean = ARIMA(log(n))) %>%
  interpolate(ace_monthly_count_pre_cv19)

ace_monthly_quantity_gp_pre_cv19 <- 
  ace_monthly_quantity_gp_pre_cv19%>% 
  group_by(regional_unit) %>% 
  model(mean = ARIMA(log(n))) %>% 
  interpolate(ace_monthly_quantity_gp_pre_cv19)

@@

```{r, ace-gp-practice-modelling}
plan(cluster)
system.time(ace_gp_cv_models <-
  ace_monthly_quantity_gp_pre_cv19 %>%
                  regionalCV(init = 36, step = 3))
plan(sequential)

ace_gp_cv_models %>%
  saveRDS("../../data/ace_gp_cv_models.rds")

ace_gp_cv_models <- 
  read_rds("../../data/ace_gp_cv_models.rds")

ace_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  rankModels() %>% 
  slice(1, .preserve = TRUE) %>% 
  ggplot(aes(x = MAPE)) +
  geom_histogram() +
  xlim(0,100)

ace_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  rankModels() %>% 
  slice(1, .preserve = TRUE) %>% 
  group_by(.model) %>% 
  count() %>% 
  arrange(desc(n))

@@

```{r ace-gp-modelling-accuracy}
best_model_gp <- 
  ace_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  rankModels() %>% 
  slice(1, .preserve = TRUE)

@@

```{r ace-gp-practice-forecasts}
plan(cluster)
system.time(ace_gp_fcsts <-
              ace_monthly_quantity_gp_pre_cv19 %>%
              filter(!regional_unit %in% best_mape_over_50$regional_unit) %>%
              regionalJointFcsts(h = "8 months"))
plan(sequential)

ace_gp_fcsts %>%
  saveRDS("../../data/ace_gp_fcsts.rds")

ace_gp_fcsts <- 
  read_rds("../../data/ace_gp_fcsts.rds")

@@

```{r, ace-gp-practice-discrepancies-abs}
best_model_gp <- 
  ace_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  rankModels() %>% 
  slice(1, .preserve = TRUE) %>% 
  filter(MAPE < 50)

@@

best_model_gp_discrep %>% 
  saveRDS("../../data/differences/ace_discreps.rds")
```

### 2021-03-06 r_notebooks/preparing_differences/preparing_adrenoceptor_agonists.Rmd
Edited preparing_ files. arima interpolation, init 36 months, 8 month horizon, excluded Jan and Feb 2020 from training

```{r adreno-data}
gp <- 
  read_rds("../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as_factor(practiceid)) %>% 
  ungroup() %>% 
  janitor::clean_names() %>% 
  select(practice_id, year, npat)

adreno <- 
  read_rds("../data/presdata_updates_040121/presc_wales_adrenoceptor-agonists.rds") %>% 
  mutate(datename = dmy(paste0("28-", datename))) %>% 
  janitor::clean_names()

@@

## Identify GPs with missing data 
gp_missing <- 
  adreno_monthly_quantity_gp %>% 
  as_tibble() %>% 
  pivot_wider(id_cols = regional_unit, names_from = datename,
              values_from = n, values_fill = NA) %>% 
  rowwise() %>% 
  mutate(across(.cols = `2015 Jan`:`2020 Aug`, .fns = is.na)) %>% 
  group_by(regional_unit) %>% 
  summarise(miss_non_covid = sum(c_across(`2015 Jan`:`2020 Feb`)),
            miss_covid = sum(c_across(`2020 Mar`:`2020 Aug`))) %>% 
  filter(miss_covid > 0 | miss_non_covid > 0) %>% 
  mutate(miss_10_non_covid = if_else(miss_non_covid > 62/10, TRUE, FALSE))

@@

## Sort into monthly count data pre-lockdown (March 2020) as training data
adreno_monthly_count_pre_cv19 <- 
  adreno_monthly_count %>% 
  filter(datename < yearmonth(dmy("01-03-2020")))

adreno_monthly_quantity_gp_pre_cv19 <- 
  adreno_monthly_quantity_gp %>% 
  filter(datename < yearmonth(dmy("01-03-2020")))

## Replace missing values in training data
adreno_monthly_count_pre_cv19 <- 
  adreno_monthly_count_pre_cv19 %>% 
  model(mean = MEAN(n)) %>%
  interpolate(adreno_monthly_count_pre_cv19)

adreno_monthly_quantity_gp_pre_cv19 <- 
  adreno_monthly_quantity_gp_pre_cv19%>% 
  group_by(regional_unit) %>% 
  model(mean = MEAN(n)) %>% 
  interpolate(adreno_monthly_quantity_gp_pre_cv19)

@@

```{r, adreno-gp-practice-modelling}
plan(cluster)
system.time(adreno_gp_cv_models <-
  adreno_monthly_quantity_gp_pre_cv19 %>%
                  regionalCV(init = 48, step = 3))
plan(sequential)

adreno_gp_cv_models %>%
  saveRDS("../data/adreno_gp_cv_models.rds")

adreno_gp_cv_models <- 
  read_rds("../data/adreno_gp_cv_models.rds")

adreno_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  ggplot(aes(x = MAPE)) +
  geom_histogram() +
  xlim(0,100)

adreno_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  group_by(.model) %>% 
  count() %>% 
  arrange(desc(n))

@@

```{r adreno-gp-modelling-accuracy}
best_model_gp <- 
  adreno_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE)

@@

```{r adreno-gp-practice-forecasts}
plan(cluster)
system.time(adreno_gp_fcsts <-
              adreno_monthly_quantity_gp_pre_cv19 %>%
              filter(!regional_unit %in% best_mape_over_50$regional_unit) %>%
              regionalJointFcsts(h = "6 months"))
plan(sequential)

adreno_gp_fcsts %>%
  saveRDS("../data/adreno_gp_fcsts.rds")

adreno_gp_fcsts <- 
  read_rds("../data/adreno_gp_fcsts.rds")

@@

```{r, adreno-gp-practice-discrepancies}
best_model_gp <- 
  adreno_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  filter(MAPE < 50)

@@

best_model_gp_discrep %>% 
  saveRDS("../data/differences/adreno_discreps.rds")

>>>>

```{r adreno-data}
gp <- 
  read_rds("../../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as_factor(practiceid)) %>% 
  ungroup() %>% 
  janitor::clean_names() %>% 
  select(practice_id, year, npat)

adreno <- 
  read_rds("../../data/presdata_updates_040121/presc_wales_adrenoceptor-agonists.rds") %>% 
  mutate(datename = dmy(paste0("28-", datename))) %>% 
  janitor::clean_names()

@@

## Identify GPs with missing data 
gp_missing <- 
  adreno_monthly_quantity_gp %>% 
  as_tibble() %>% 
  pivot_wider(id_cols = regional_unit, names_from = datename,
              values_from = n, values_fill = NA) %>% 
  rowwise() %>% 
  mutate(across(.cols = `2015 Jan`:`2020 Aug`, .fns = is.na)) %>% 
  group_by(regional_unit) %>% 
  summarise(miss_non_covid = sum(c_across(`2015 Jan`:`2020 Feb`)),
            miss_covid = sum(c_across(`2020 Mar`:`2020 Aug`))) %>% 
  filter(miss_covid > 0 | miss_non_covid > 0) %>% 
  mutate(miss_10_non_covid = if_else(miss_non_covid > 60/10, TRUE, FALSE))

@@

## Sort into monthly count data pre-lockdown (March 2020) as training data
adreno_monthly_count_pre_cv19 <- 
  adreno_monthly_count %>% 
  filter(datename < yearmonth(dmy("01-01-2020")))

adreno_monthly_quantity_gp_pre_cv19 <- 
  adreno_monthly_quantity_gp %>% 
  filter(datename < yearmonth(dmy("01-01-2020")))

## Replace missing values in training data
adreno_monthly_count_pre_cv19 <- 
  adreno_monthly_count_pre_cv19 %>% 
  model(arima = ARIMA(n)) %>%
  interpolate(adreno_monthly_count_pre_cv19)

adreno_monthly_quantity_gp_pre_cv19 <- 
  adreno_monthly_quantity_gp_pre_cv19%>% 
  group_by(regional_unit) %>% 
  model(arima = ARIMA(n)) %>% 
  interpolate(adreno_monthly_quantity_gp_pre_cv19)

@@

```{r, adreno-gp-practice-modelling}
plan(cluster)
system.time(adreno_gp_cv_models <-
  adreno_monthly_quantity_gp_pre_cv19 %>%
                  regionalCV(init = 36, step = 3))
plan(sequential)

adreno_gp_cv_models %>%
  saveRDS("../../data/adreno_gp_cv_models.rds")

adreno_gp_cv_models <- 
  read_rds("../../data/adreno_gp_cv_models.rds")

adreno_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  rankModels() %>% 
  slice(1, .preserve = TRUE) %>% 
  ggplot(aes(x = MAPE)) +
  geom_histogram() +
  xlim(0,100)

adreno_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  rankModels() %>% 
  slice(1, .preserve = TRUE) %>% 
  group_by(.model) %>% 
  count() %>% 
  arrange(desc(n))

@@

```{r adreno-gp-modelling-accuracy}
best_model_gp <- 
  adreno_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  rankModels() %>% 
  slice(1, .preserve = TRUE)

@@

```{r adreno-gp-practice-forecasts}
plan(cluster)
system.time(adreno_gp_fcsts <-
              adreno_monthly_quantity_gp_pre_cv19 %>%
              filter(!regional_unit %in% best_mape_over_50$regional_unit) %>%
              regionalJointFcsts(h = "8 months"))
plan(sequential)

adreno_gp_fcsts %>%
  saveRDS("../../data/adreno_gp_fcsts.rds")

adreno_gp_fcsts <- 
  read_rds("../../data/adreno_gp_fcsts.rds")

@@

```{r, adreno-gp-practice-discrepancies}
best_model_gp <- 
  adreno_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  rankModels() %>% 
  slice(1, .preserve = TRUE) %>% 
  filter(MAPE < 50)

@@

best_model_gp_discrep %>% 
  saveRDS("../../data/differences/adreno_discreps.rds")

### 2021-03-06 r_notebooks/preparing_differences/preparing_all_prescribing.Rmd
Edited preparing_ files. arima interpolation, init 36 months, 8 month horizon, excluded Jan and Feb 2020 from training

```{r all-prescribing-data}
gp <- 
  read_rds("../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as_factor(practiceid)) %>% 
  ungroup() %>% 
  janitor::clean_names() %>% 
  select(practice_id, year, npat)

all_prescribing <- 
  read_csv("../data/all_prescribing.csv", col_names = c("n", "datename")) %>% 
  mutate(datename = dmy(paste(28, datename, sep = "-")),
         datename = yearmonth(datename),
         regional_unit = factor("all")) %>% 
  as_tsibble(index = datename)

## Sort into monthly count data pre-lockdown (March 2020) as training data
all_prescribing_pre_cv19 <- 
  all_prescribing %>% 
  filter(datename < yearmonth(dmy("01-03-2020")))

@@

all_prescribing_fable_models <- 
  all_prescribing_pre_cv19 %>% 
  mutate(datename = yearmonth(datename)) %>%
  fill_gaps() %>%
  slice(1:(n()-6), .preserve = TRUE) %>%
  stretch_tsibble(.init = 36, .step = 3) %>%
  fableModels()

all_prescribing_fable_forecasts <- 
  fable_models %>%
  forecast(h = 6)

all_prescribing_fable_fits <- 
  fable_forecasts %>% 
  accuracy(all_prescribing_pre_cv19, list(RMSE = RMSE, MAE = MAE, MAPE = MAPE,
                           rmse_skill = skill_score(RMSE),
                           crps_skill = skill_score(CRPS), ACF1 =ACF1,
                           winkler = winkler_score))

all_prescribing_prophet_fits <- 
  all_prescribing_pre_cv19 %>%
  mutate(datename = yearmonth(datename)) %>%
  fill_gaps() %>%
  slice(1:(n()-6), .preserve = TRUE) %>%
  stretch_tsibble(.init = 36, .step = 3) %>%
  prophetModels() %>%
  forecast(h = 6) %>%
  accuracy(all_prescribing_pre_cv19, list(RMSE = RMSE, MAE = MAE, MAPE = MAPE,
                           rmse_skill = skill_score(RMSE),
                           crps_skill = skill_score(CRPS), ACF1 =ACF1,
                           winkler = winkler_score))

all_prescribing_combined_fits <- 
  bind_rows(all_prescribing_fable_fits, all_prescribing_prophet_fits) %>%
  arrange(RMSE, MAE)
plan(sequential)

@@

all_prescribing_cv_models %>%
  saveRDS("../data/all_prescribing_cv_models.rds")

all_prescribing_cv_models <- 
  read_rds("../data/all_prescribing_cv_models.rds")

all_prescribing_cv_models %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  ggplot(aes(x = MAPE)) +
  geom_histogram()

all_prescribing_cv_models %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  group_by(.model) %>% 
  count() %>% 
  arrange(desc(n))

@@

```{r all-prescribing-modelling-accuracy}
best_model <- 
  all_prescribing_cv_models %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE)
```

```{r all-prescribing-practice-forecasts}
plan(cluster)
all_prescribing_fcsts <-
  all_prescribing_pre_cv19 %>%
  regionalJointFcsts(h = "6 months")
plan(sequential)

all_prescribing_fcsts %>%
  saveRDS("../data/all_prescribing_fcsts.rds")

all_prescribing_fcsts <- 
  read_rds("../data/all_prescribing_fcsts.rds")

@@

best_model_discrep %>% 
  saveRDS("../data/differences/all_prescribing_discreps.rds")

>>>>

```{r all-prescribing-data}
gp <- 
  read_rds("../../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as_factor(practiceid)) %>% 
  ungroup() %>% 
  janitor::clean_names() %>% 
  select(practice_id, year, npat)

all_prescribing <- 
  read_csv("../../data/all_prescribing.csv", col_names = c("n", "datename")) %>% 
  mutate(datename = dmy(paste(28, datename, sep = "-")),
         datename = yearmonth(datename),
         regional_unit = factor("all")) %>% 
  as_tsibble(index = datename)

## Sort into monthly count data pre-lockdown (March 2020) as training data
all_prescribing_pre_cv19 <- 
  all_prescribing %>% 
  filter(datename < yearmonth(dmy("01-01-2020")))

@@

all_prescribing_fable_models <- 
  all_prescribing_pre_cv19 %>% 
  mutate(datename = yearmonth(datename)) %>%
  fill_gaps() %>%
  slice(1:(n()-8), .preserve = TRUE) %>%
  stretch_tsibble(.init = 36, .step = 3) %>%
  fableModels()

all_prescribing_fable_forecasts <- 
  all_prescribing_fable_models %>%
  forecast(h = 8)

all_prescribing_fable_fits <- 
  all_prescribing_fable_forecasts %>% 
  accuracy(all_prescribing_pre_cv19, list(RMSE = RMSE, MAE = MAE, MAPE = MAPE,
                           rmse_skill = skill_score(RMSE),
                           crps_skill = skill_score(CRPS), ACF1 =ACF1,
                           winkler = winkler_score))

all_prescribing_prophet_fits <- 
  all_prescribing_pre_cv19 %>%
  mutate(datename = yearmonth(datename)) %>%
  fill_gaps() %>%
  slice(1:(n()-8), .preserve = TRUE) %>%
  stretch_tsibble(.init = 36, .step = 3) %>%
  prophetModels() %>%
  forecast(h = 8) %>%
  accuracy(all_prescribing_pre_cv19, list(RMSE = RMSE, MAE = MAE, MAPE = MAPE,
                           rmse_skill = skill_score(RMSE),
                           crps_skill = skill_score(CRPS), ACF1 =ACF1,
                           winkler = winkler_score))

all_prescribing_combined_fits <- 
  bind_rows(all_prescribing_fable_fits, all_prescribing_prophet_fits) %>%
  rankModels()
plan(sequential)

@@

all_prescribing_cv_models %>%
  saveRDS("../../data/all_prescribing_cv_models.rds")

all_prescribing_cv_models <- 
  read_rds("../../data/all_prescribing_cv_models.rds")

all_prescribing_cv_models %>% 
  rankModels() %>% 
  slice(1, .preserve = TRUE) %>% 
  ggplot(aes(x = MAPE)) +
  geom_histogram()

all_prescribing_cv_models %>% 
  rankModels() %>% 
  slice(1, .preserve = TRUE) %>% 
  group_by(.model) %>% 
  count() %>% 
  arrange(desc(n))

@@

```{r all-prescribing-modelling-accuracy}
best_model <- 
  all_prescribing_cv_models %>% 
  rankModels() %>% 
  slice(1, .preserve = TRUE)
```

```{r all-prescribing-practice-forecasts}
plan(cluster)
all_prescribing_fcsts <-
  all_prescribing_pre_cv19 %>%
  regionalJointFcsts(h = "8 months")
plan(sequential)

all_prescribing_fcsts %>%
  saveRDS("../../data/all_prescribing_fcsts.rds")

all_prescribing_fcsts <- 
  read_rds("../../data/all_prescribing_fcsts.rds")

@@

best_model_discrep %>% 
  saveRDS("../../data/differences/all_prescribing_discreps.rds")

### 2021-03-06 r_notebooks/preparing_differences/preparing_azithro.Rmd
Edited preparing_ files. arima interpolation, init 36 months, 8 month horizon, excluded Jan and Feb 2020 from training

```{r azithro-data}
gp <- 
  read_rds("../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as_factor(practiceid)) %>% 
  ungroup() %>% 
  janitor::clean_names() %>% 
  select(practice_id, year, npat)

azithro <- 
  read_rds("../data/presdata_updates_040121/presc_wales_azithromycin.rds") %>% 
  janitor::clean_names() %>% 
  mutate(datename = dmy(paste0("28-", datename)),
         practice_id = as_factor(practiceid))

@@

## Identify GPs with missing data 
gp_missing <- 
  azithro_monthly_quantity_gp %>% 
  as_tibble() %>% 
  pivot_wider(id_cols = regional_unit, names_from = datename,
              values_from = n, values_fill = NA) %>% 
  rowwise() %>% 
  mutate(across(.cols = `2015 Jan`:`2020 Aug`, .fns = is.na)) %>% 
  group_by(regional_unit) %>% 
  summarise(miss_non_covid = sum(c_across(`2015 Jan`:`2020 Feb`)),
            miss_covid = sum(c_across(`2020 Mar`:`2020 Aug`))) %>% 
  filter(miss_covid > 0 | miss_non_covid > 0) %>% 
  mutate(miss_10_non_covid = if_else(miss_non_covid > 62/10, TRUE, FALSE))

@@

## Sort into monthly count data pre-lockdown (March 2020) as training data
azithro_monthly_count_pre_cv19 <- 
  azithro_monthly_count %>% 
  filter(datename < yearmonth(dmy("01-03-2020")))

azithro_monthly_quantity_gp_pre_cv19 <- 
  azithro_monthly_quantity_gp %>% 
  filter(datename < yearmonth(dmy("01-03-2020")))

## Replace missing values in training data
azithro_monthly_count_pre_cv19 <- 
  azithro_monthly_count_pre_cv19 %>% 
  model(mean = MEAN(n)) %>%
  interpolate(azithro_monthly_count_pre_cv19)

azithro_monthly_quantity_gp_pre_cv19 <- 
  azithro_monthly_quantity_gp_pre_cv19%>% 
  group_by(regional_unit) %>% 
  model(mean = MEAN(n)) %>% 
  interpolate(azithro_monthly_quantity_gp_pre_cv19)

@@

```{r, azithro-gp-practice-modelling}
# plan(cluster)
# system.time(azithro_gp_cv_models <-
#   azithro_monthly_quantity_gp_pre_cv19 %>%
#                   regionalCV(init = 48, step = 3))
# plan(sequential)
# 
# azithro_gp_cv_models %>%
#   saveRDS("../data/azithro_gp_cv_models.rds")

azithro_gp_cv_models <- 
  read_rds("../data/azithro_gp_cv_models.rds")

azithro_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  ggplot(aes(x = MAPE)) +
  geom_histogram() +
  xlim(0,100)

azithro_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  group_by(.model) %>% 
  count() %>% 
  arrange(desc(n))

@@

```{r azithro-gp-modelling-accuracy}
best_model_gp <- 
  azithro_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE)

@@

```{r azithro-gp-practice-forecasts}
# plan(cluster)
# system.time(azithro_gp_fcsts <-
#               azithro_monthly_quantity_gp_pre_cv19 %>%
#               filter(!regional_unit %in% best_mape_over_50$regional_unit) %>%
#               regionalJointFcsts(h = "6 months"))
# plan(sequential)
# 
# azithro_gp_fcsts %>%
#   saveRDS("../data/azithro_gp_fcsts.rds")

azithro_gp_fcsts <- 
  read_rds("../data/azithro_gp_fcsts.rds")

@@

```{r, azithro-gp-practice-discrepancies}
best_model_gp <- 
  azithro_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  arrange(RMSE, MAE) %>% 
  slice(1, .preserve = TRUE) %>% 
  filter(MAPE < 50)

@@

best_model_gp_discrep %>% 
  saveRDS("../data/differences/azithro_discreps.rds")

>>>>

```{r azithro-data}
gp <- 
  read_rds("../../OneDrive/2_interimdata/8_linkeddata/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as_factor(practiceid)) %>% 
  ungroup() %>% 
  janitor::clean_names() %>% 
  select(practice_id, year, npat)

azithro <- 
  read_rds("../../data/presdata_updates_040121/presc_wales_azithromycin.rds") %>% 
  janitor::clean_names() %>% 
  mutate(datename = dmy(paste0("28-", datename)),
         practice_id = as_factor(practiceid))

@@

## Identify GPs with missing data 
gp_missing <- 
  azithro_monthly_quantity_gp %>% 
  as_tibble() %>% 
  pivot_wider(id_cols = regional_unit, names_from = datename,
              values_from = n, values_fill = NA) %>% 
  rowwise() %>% 
  mutate(across(.cols = `2015 Jan`:`2020 Aug`, .fns = is.na)) %>% 
  group_by(regional_unit) %>% 
  summarise(miss_non_covid = sum(c_across(`2015 Jan`:`2020 Feb`)),
            miss_covid = sum(c_across(`2020 Mar`:`2020 Aug`))) %>% 
  filter(miss_covid > 0 | miss_non_covid > 0) %>% 
  mutate(miss_10_non_covid = if_else(miss_non_covid > 60/10, TRUE, FALSE))

@@

## Sort into monthly count data pre-lockdown (March 2020) as training data
azithro_monthly_count_pre_cv19 <- 
  azithro_monthly_count %>% 
  filter(datename < yearmonth(dmy("01-01-2020")))

azithro_monthly_quantity_gp_pre_cv19 <- 
  azithro_monthly_quantity_gp %>% 
  filter(datename < yearmonth(dmy("01-01-2020")))

## Replace missing values in training data
azithro_monthly_count_pre_cv19 <- 
  azithro_monthly_count_pre_cv19 %>% 
  model(arima = ARIMA(n)) %>%
  interpolate(azithro_monthly_count_pre_cv19)

azithro_monthly_quantity_gp_pre_cv19 <- 
  azithro_monthly_quantity_gp_pre_cv19%>% 
  group_by(regional_unit) %>% 
  model(arima = ARIMA(n)) %>% 
  interpolate(azithro_monthly_quantity_gp_pre_cv19)

@@

```{r, azithro-gp-practice-modelling}
# plan(cluster)
# system.time(azithro_gp_cv_models <-
#   azithro_monthly_quantity_gp_pre_cv19 %>%
#                   regionalCV(init = 36, step = 3))
# plan(sequential)
# 
# azithro_gp_cv_models %>%
#   saveRDS("../../data/azithro_gp_cv_models.rds")

azithro_gp_cv_models <- 
  read_rds("../../data/azithro_gp_cv_models.rds")

azithro_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  rankModels() %>% 
  slice(1, .preserve = TRUE) %>% 
  ggplot(aes(x = MAPE)) +
  geom_histogram() +
  xlim(0,100)

azithro_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  rankModels() %>% 
  slice(1, .preserve = TRUE) %>% 
  group_by(.model) %>% 
  count() %>% 
  arrange(desc(n))

@@

```{r azithro-gp-modelling-accuracy}
best_model_gp <- 
  azithro_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  rankModels() %>% 
  slice(1, .preserve = TRUE)

@@

```{r azithro-gp-practice-forecasts}
# plan(cluster)
# system.time(azithro_gp_fcsts <-
#               azithro_monthly_quantity_gp_pre_cv19 %>%
#               filter(!regional_unit %in% best_mape_over_50$regional_unit) %>%
#               regionalJointFcsts(h = "8 months"))
# plan(sequential)
# 
# azithro_gp_fcsts %>%
#   saveRDS("../../data/azithro_gp_fcsts.rds")

azithro_gp_fcsts <- 
  read_rds("../../data/azithro_gp_fcsts.rds")

@@

```{r, azithro-gp-practice-discrepancies}
best_model_gp <- 
  azithro_gp_cv_models %>% 
  group_by(regional_unit) %>% 
  rankModels() %>% 
  slice(1, .preserve = TRUE) %>% 
  filter(MAPE < 50)

@@

best_model_gp_discrep %>% 
  saveRDS("../../data/differences/azithro_discreps.rds")
